%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xcolor} % for blue links
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue]{hyperref} % updated for blue links
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\ % MODIFIED: Removed \textit{\small} from #3 and #4 to match the standard font of #2 (location/city)
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Neha Gaikwad} \\ \vspace{1pt}
    \small 
    +91 8591742120 $|$ \href{mailto:nehagaikwadwork24@gmail.com}{nehagaikwadwork24@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/neha-gaikwad-56449b347/}{linkedin.com/in/nehagaikwad} $|$
    \href{https://github.com/NehaaGaikwad}{github.com/NehaaGaikwad} \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

    \resumeSubheading
        {Vidyalankar Institute of Technology}{Mumbai, India}
        {Bachelor of Technology in Computer Engineering}{Sept 2024 -- Present} % REMOVED \normalsize
    \resumeItemListStart
        \resumeItem{CGPA: \textbf{9.9} (First Year), SGPA: \textbf{10.0} (Sem 3)}
        \resumeItem{Expected Graduation: \textbf{2028}}
    \resumeItemListEnd

    \resumeSubheading
        {Arya Gurukul (CBSE Board)}{Kalyan, India}
        {Class X}{2022}
    \resumeItemListStart
        \resumeItem{Percentage: \textbf{95\%}}
    \resumeItemListEnd

    \resumeSubheading
        {R.T.P College (State Board)}{Dombivli, India}
        {Class XII}{2024}
    \resumeItemListStart
        \resumeItem{Percentage: \textbf{81.83\%}}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

% -----------EXTRACURRICULAR ACTIVITY-----------
\section{Extracurricular Activity}
\resumeSubHeadingListStart

    \resumeSubheading
        {Open Source Contributions}{Open World Holidays Framework}{Contributor}{2025}
    \resumeItemListStart
        \resumeItem{Translated \textbf{Nepali and Bangladeshi holidays} for all public holidays, ensuring \textbf{correct regional names}.}
        \resumeItem{Maintained \textbf{tests} and collaborated with \textbf{global maintainers} to ensure proper integration and consistency.}
        \resumeItem{Gained hands-on experience with \textbf{Git, pull requests, code reviews}, and contributing to a widely used \textbf{open-source project}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-4pt} % small gap before first project
\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{\normalsize{Weather Forecast Application}} $|$ \emph{Python, Tkinter, OpenWeather API, Geopy, TimezoneFinder}}%
    {\href{https://github.com/NehaaGaikwad/Weather-Forecast}{GitHub}}
\resumeItemListStart
    \resumeItem{Developed a \textbf{Tkinter-based weather app} showing real-time weather and 5-day forecasts worldwide.}
    \resumeItem{Integrated \textbf{geolocation} and \textbf{timezone detection} for accurate local time and coordinates.}
    \resumeItem{Displayed \textbf{temperature, pressure, wind speed, and dynamic icons} in a clean UI.}
\resumeItemListEnd
\vspace{5pt} % small gap after project

\resumeProjectHeading
    {\textbf{\normalsize{Aim Trainer Game}} $|$ \emph{Python, Pygame}}%
    {\href{https://github.com/NehaaGaikwad/Aim-Trainer}{GitHub}}
\resumeItemListStart
    \resumeItem{Developed a \textbf{Pygame-based aim trainer} to improve reaction time and targeting skills.}
    \resumeItem{Implemented dynamic targets with \textbf{growing/shrinking mechanics}, scoring, and limited lives.}
    \resumeItem{Displayed real-time statistics: \textbf{hits, accuracy, speed, and elapsed time} in a clean UI.}
\resumeItemListEnd
\vspace{5pt} % small gap after project

\resumeProjectHeading
    {\textbf{\normalsize{Turtle Race Game}} $|$ \emph{Python, Turtle}}%
    {\href{https://github.com/NehaaGaikwad/Turtle-Race}{GitHub}}
\resumeItemListStart
    \resumeItem{Built an interactive \textbf{Python Turtle racing game} with 2–10 customizable racers.}
    \resumeItem{Implemented random movement mechanics to simulate racing and determine the winner dynamically.}
    \resumeItem{Designed a visual interface using \textbf{Turtle graphics} with multiple colored racers and race track.}
    \resumeItemListEnd
\vspace{5pt} % small gap after project

\resumeProjectHeading
    {\textbf{\normalsize{QR Code Generator}} $|$ \emph{Python, Flask, qrcode, HTML}}%
    {\href{https://github.com/NehaaGaikwad/QR_Code-Generator}{GitHub}}
\resumeItemListStart
    \resumeItem{Developed a \textbf{Flask-based web application} to generate QR codes from user-provided links.}
    \resumeItem{Used \textbf{qrcode} and \textbf{BytesIO} to create QR code images dynamically in memory.}
    \resumeItem{Rendered the QR code on a web page using \textbf{HTML templates} and embedded base64 images.}
\resumeItemListEnd
\vspace{5pt} % small gap after project

\resumeProjectHeading
    {\textbf{\normalsize{Amazon Clone Homepage}} $|$ \emph{HTML, CSS, Font Awesome}}%
    {\href{https://github.com/NehaaGaikwad/Amazon-clone}{GitHub}}
\resumeItemListStart
    \resumeItem{Built a \textbf{static Amazon homepage clone} to practice layout design using only HTML and CSS.}
    \resumeItem{Implemented \textbf{navbar, hero section, product boxes, and footer} with clean grid layout.}
    \resumeItem{Added \textbf{Font Awesome icons}, hover effects, and organized images folder for easy editing.}
    \resumeItem{Designed a \textbf{simple and visually neat UI} closely resembling Amazon’s homepage.}
    \resumeItem{Future plan: add JavaScript for interactivity and responsive design improvements.}
\resumeItemListEnd
\vspace{5pt} % small gap after project

\resumeSubHeadingListEnd

% -----------SKILLS-----------
\section{Skills}
\vspace{-2pt}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item{
        \begin{tabular}{ l@{\hskip 0.3in} l }
            \textbf{Languages} : C, Python, Java, MySQL, HTML, CSS \\
            \textbf{Developer Tools} : Git, GitHub, VS Code \\
        \end{tabular}
    }
\end{itemize}

%-------------------------------------------
\end{document}